%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

%% AltaCV uses the fontawesome5 and academicons fonts
%% and packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=0.75cm, right=0.75cm, top=0.8cm, bottom=0.6cm, columnsep=0.55cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}
\usepackage[dvipsnames]{xcolor}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Akhil Nadigatla}
% \tagline{Your Position or Tagline Here}
%% You can add multiple photos on the left or right
% \photoR{2.8cm}{Globe_High}
% \photoL{2.5cm}{Yacht_High,Suitcase_High}

\personalinfo{%
  % Not all of these are required!
  \href{mailto:akhilnadigatla@cmu.edu}{\email{akhilnadigatla@cmu.edu}}
  \phone{412-482-8967}
  % \mailaddress{Åddrésş, Street, 00000 Cóuntry}
  % \location{Pittsburgh, PA}
  \href{https://akhilnadigatla.com/}{\homepage{akhilnadigatla.com}}
  % \twitter{@twitterhandle}
  \href{linkedin.com/in/akhil-nadigatla/}{\linkedin{akhil-nadigatla}}
  \href{https://github.com/akhilnadigatla}{\github{akhilnadigatla}}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
  % \orcid{0000-0000-0000-0000}
  %% You can add your own arbtrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  \NewInfoField{gitlab}{\faPhone}[https://gitlab.com/]
}

\makecvheader
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.63}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Work Experience}

\cvevent{Software Engineer Intern | {\small Java, AWS, GCP}}{Splunk}{June 2021 - August 2021}{San Jose, CA}
\begin{itemize}
\item Worked on Observability Cloud Analytics team to improve real-time streaming capacities and efficiency of platform that drives all metric transformations processed by SignalFx product.
\item Developed novel workflow for large window, fine resolution tasks that increased capacity by \textasciitilde3,500\% and cut job migration and restart times by \textasciitilde700\% by offshoring window data to external persistence.
\end{itemize}

\vspace{-5pt}
\divider
\vspace{-5pt}

\cvevent{Web Development and Support Lead | {\small JavaScript, AWS}}{CS Academy}{May 2019 - December 2019}{Pittsburgh, PA}
\begin{itemize}
\item Drove content creation, testing, and development of free platform for learning computer science principles. Led development of features that improved ease-of-use, achieving a five-fold increase in active users.
\end{itemize}

\cvsection{Research}

\cvevent{{\href{}{Towards Efficient Neural Zeroth-Order Optimization Algorithms}}}{CMU Machine Learning Department}{August 2021 - present}{Pittsburgh, PA}
\begin{itemize}
    \item Advised by \href{http://www.cs.cmu.edu/~pradeepr/}{\textcolor{Mahogany}{Prof. Ravikumar}} for honors senior thesis program, investigating more efficient derivative-free optimization techniques in high-dimensional settings without any assumptions about the underlying objective function.
\end{itemize}

\vspace{-5pt}
\divider
\vspace{-5pt}

\cvevent{{\href{https://akhilnadigatla.com/assets/docs/15400-final-report.pdf}{Adversarial Robustness via Model Ensembles}}}{CMU Machine Learning Department}{October 2020 - May 2021}{Pittsburgh, PA}
\begin{itemize}
    \item Under the mentorship of \href{http://www.cs.cmu.edu/~pradeepr/}{\textcolor{Mahogany}{Prof. Ravikumar}}, evaluated effects of weighted ensembles of classifiers on adversarial robustness of deep neural networks.
    \item Witnessed a 1 to 2\% (statistically significant) improvement in accuracy on perturbed samples from MNIST and CIFAR-10 datasets.
\end{itemize}

\cvsection{Selected Projects}

\cvevent{SafeEvents | {\small Python, Firebase}}{}{August 2020 - November 2020}{}
\begin{itemize}
\item Developed mobile event tracking application providing COVID-19 risk estimates by locality using active data from Georgia Tech project.
\item Used at Univ. of Minnesota - Twin Cities and UT - Austin.
\end{itemize}

\vspace{-5pt}
\divider
\vspace{-5pt}

\cvevent{Dendrogram Generator | {\small R}}{}{June 2020 - August 2020}{Nairobi, Kenya}
\begin{itemize}
\item Created pipeline to convert DNA marker information for different crop varieties into dendrograms to aid in trait association, all wrapped in a GUI.
\item Currently in use at International Institute for Tropical Agriculture.
\end{itemize}

\vspace{-5pt}
\divider
\vspace{-5pt}

\cvevent{ConvoCoach | {\small Python, GCP}}{}{March 2019 - June 2019}{}
\begin{itemize}
\item Developed application, along with four colleagues, to assist and improve the capabilities of autistic individuals with daily conversations.
\item Utilized cloud NLP, image association, speech recognition and synthesis tools to drive predictive, dynamic conversations.
\end{itemize}

\medskip

% use ONLY \newpage if you want to force a page break for
% ONLY the current column

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Education}

\cvevent{B.Sc.\ in Computer Science}{Carnegie Mellon University}{August 2018 - May 2022 (expected)}{}
GPA: 3.48 \\
Major: Computer Science \\
Minors: Machine Learning, Philosophy

\cvsection{Coursework}

\begin{itemize}
\item Distributed Systems (15-440)
\item Algorithm Design and Analysis (15-451)
\item Machine Learning (10-315)
\item Software Engineering (17-313)
\item Programming Languages (15-312)
\item Parallel Data Structures \& Algos (15-210)
\item Computer Systems (15-213)
\item Theoretical CS (15-251)
\end{itemize}

\cvsection{Teaching}

\begin{itemize}
\item Research and Innovation in CS (15-300)
\end{itemize}

\cvsection{Skills}

\cvtag{Python}
\cvtag{C}
\cvtag{C++}
\cvtag{Java}
\cvtag{SML} \\
\cvtag{JavaScript/TypeScript}

\divider

\cvtag{PyTorch}
\cvtag{Tensorflow}
\cvtag{JAX}
\cvtag{Spark}
\cvtag{React}
\cvtag{MongoDB}
\cvtag{Git}
\cvtag{\LaTeX}

\divider

\cvtag{AWS}
\cvtag{GCP}
\cvtag{Docker}
\cvtag{CI/CD}
\cvtag{Agile}

%% Yeah I didn't spend too much time making all the
%% spacing consistent... sorry. Use \smallskip, \medskip,
%% \bigskip, \vpsace etc to make adjustments.

\cvsection{Achievements}

\cvachievement{\faTrophy}{Putnam Math Competition}{Top 500 (out of \textasciitilde4000)}

\divider

\cvachievement{\faTrophy}{CMU SCS Dean's List}{High Honors (F'20, F'21)}

\divider

\cvachievement{\faTrophy}{TartanHacks}{Best Social Welfare Hack}

\divider

\cvachievement{\faTrophy}{President's Award of Kenya}{Gold Standard (by H.E. Uhuru Kenyatta)}

\cvsection{Activities}

\begin{itemize}
\item \textbf{Atlas Autonomous Buggy} | Software Team \\ \smallskip
\textit{September 2019 - May 2020}

\item \textbf{Business Technology Club} \\ \smallskip
\textit{January 2019 - May 2019}

\item \textbf{South Asian SA} | Student Representative \\ \smallskip
\textit{September 2018 - May 2019}
\end{itemize}

\end{paracol}

\end{document}
